---
title: "Database - Maternal Obesity"
author: "Lea Seep"
date: "2023-03-31"
output: 
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 5
---

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
library(DT)
library(SummarizedExperiment)

# Read in all necassary data to display
Transcriptome <- readRDS("transcriptome_analysis/Transcriptomics_results.rds")
Transcriptome_CoCena_KC <- readRDS("transcriptome_analysis/Transcriptomics_ORA_CoCena_results_KC.rds")
Transcriptome_CoCena_HC <- readRDS("transcriptome_analysis/Transcriptomics_ORA_CoCena_results_HC.rds")

Metabolome <- readRDS("metabolome_analysis/Metabolomics_results.rds")
lipidome <- readRDS("lipidome_analysis/Lipidomic_stats_result.rds")

# Read in original Objects for transcriptome for addtional Information
DESeq_Obj_KC_ko <- readRDS("data/DESeq_Obj_KC.rds")
DESeq_Obj_HC_ko <- readRDS("data/DESeq_Obj_HC.rds")
rownames(DESeq_Obj_KC_ko) <- gsub("\\..*","",rownames(DESeq_Obj_KC_ko))
rownames(DESeq_Obj_HC_ko) <- gsub("\\..*","",rownames(DESeq_Obj_HC_ko))

```

## Overview
This document was created to facilitate an easy look up of the actual data used
within the publication. All presented tables can be filtered, searched, sorted
and downloaded in your desired output format.
We hope that this opens the door for easy data reuse!
  
## How to use
This is a html file and can be open within a browser. 
You can see on the top left the entire content of the document. If clicking
on a top potential subcategories will drop out and you can also click on one
of those to navigate to the section of interest.
The tables display most often entitie-wise information, always annotated with
all available information as well. Note that those columns are attached by default 
to the right of respective table, so you might have to scroll to see those information.
You can use drag and drop to reorder the columns (Drag the column header!).

Each column can be searched by typing into the box just underneath each column
header. If numerical values are present you can specify to see everything below
or above a certain threshold. If you click now on your desired table format to
download that certain selection will be downloaded.

If you want to download the entire table you need to check if nothing is selected (default).

# Results {.tabset}
## Transcriptomics 
### DE KC Hif1a
Results of DE-Analysis, cut down to the top 1000 genes (sorted by unadj. p-value).
```{r DE KC Hif1a, echo=FALSE}
Transcriptome$dds_KC$GeneID <- rownames(Transcriptome$dds_KC)
rownames(Transcriptome$dds_KC) <- Transcriptome$dds_KC$GeneID
Transcriptome$dds_KC$GeneID <- NULL
res <- as.data.frame(Transcriptome$dds_KC)

add_data <- rowData(DESeq_Obj_KC_ko)

data2show <- cbind(
  res,
  add_data[rownames(res),c("SYMBOL","GENETYPE")]
  )

data2show <- data2show[order(data2show$pvalue)[1:1000],]

DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
#### ORA results
```{r echo=FALSE}
UP <- Transcriptome$ORA_KC$UP
DOWN <- Transcriptome$ORA_KC$UP
```

##### KEGG
###### UP
```{r echo=FALSE}
data2show <- as.data.frame(UP$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### DOWN

```{r echo=FALSE}
data2show <- as.data.frame(DOWN$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
##### GO
###### Up
```{r echo=FALSE}
data2show <- as.data.frame(UP$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### Down
```{r echo=FALSE}
data2show <- as.data.frame(DOWN$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
##### HALLMARK
###### UP
```{r echo=FALSE}
data2show <- as.data.frame(UP$HALLMARK)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### DOWN
```{r echo=FALSE}
data2show <- as.data.frame(DOWN$HALLMARK)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```

### DE HC Hif1a
```{r DE HC Hif1a, echo=FALSE}
Transcriptome$dds_HC$GeneID <- rownames(Transcriptome$dds_HC)
rownames(Transcriptome$dds_HC) <- Transcriptome$dds_HC$GeneID
Transcriptome$dds_HC$GeneID <- NULL
res <- as.data.frame(Transcriptome$dds_HC,make.names=T)

add_data <- rowData(DESeq_Obj_HC_ko)

data2show <- cbind(
  res,
  add_data[rownames(res),c("SYMBOL","GENETYPE")]
  )

data2show <- data2show[order(data2show$pvalue)[1:1000],]

DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```

#### ORA results
```{r echo=FALSE}
UP <- Transcriptome$ORA_HC$UP
DOWN <- Transcriptome$ORA_HC$UP
```
##### KEGG
###### UP
```{r echo=FALSE}
data2show <- as.data.frame(UP$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### DOWN

```{r echo=FALSE}
data2show <- as.data.frame(DOWN$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
##### GO
###### Up
```{r echo=FALSE}
data2show <- as.data.frame(UP$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### Down
```{r echo=FALSE}
data2show <- as.data.frame(DOWN$KEGG)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
##### HALLMARK
###### UP
```{r echo=FALSE}
data2show <- as.data.frame(UP$HALLMARK)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
###### DOWN
```{r echo=FALSE}
data2show <- as.data.frame(DOWN$HALLMARK)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```


### hCoCena
#### KC wt
Cluster Sets & ORA

#### KC Hif1a
Cluster Sets & ORA

```{r echo=FALSE,results='asis'}
counter = 0

#htmltools::tagList(datatable(matrix()))
for(i in names(Transcriptome_CoCena_KC)){
  for(j in names(Transcriptome_CoCena_KC[[i]])){
    counter = counter + 1
      data2show <- Transcriptome_CoCena_KC[[i]][[j]]
      
      customCaption = paste0("Table ",counter,": Cluster: ",i," ",j," enrichment results")
      
      print(htmltools::tagList(
        DT::datatable(
          data2show,
           caption = customCaption,
          extensions = c('Buttons','ColReorder'),
          filter = 'top',
          options = list(
            pageLength = 5,
            paging = TRUE,
            searching = TRUE,
            fixedColumns = TRUE,
            colReorder = TRUE,
            autoWidth = TRUE,
            ordering = TRUE,
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel')
        ),
        class = "display"
      ))
      )
  }
}

```

#### HC Hif1a
Cluster Sets & ORA
```{r echo=FALSE,results='asis'}
counter = 0
#htmltools::tagList(datatable(matrix()))
for(i in names(Transcriptome_CoCena_HC)){
  for(j in names(Transcriptome_CoCena_HC[[i]])){
    counter = counter + 1
      data2show <- Transcriptome_CoCena_HC[[i]][[j]]
      
      customCaption = paste0("Table ",counter,": Cluster: ",i," ",j," enrichment results")
      
      print(htmltools::tagList(
        DT::datatable(
          data2show,
           caption = customCaption,
          extensions = c('Buttons','ColReorder'),
          filter = 'top',
          options = list(
            pageLength = 5,
            paging = TRUE,
            searching = TRUE,
            fixedColumns = TRUE,
            colReorder = TRUE,
            autoWidth = TRUE,
            ordering = TRUE,
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel')
        ),
        class = "display"
      ))
      )
  }
}

```


## Metabolomics
### ANOVA results ko HFD CD CD vs wt HFD CD CD

```{r echo=FALSE}
data2show <- Metabolome$ANOVA_HFDCDCD_vs_CDCDCD
data2show <- data2show[,!grepl("^FS",colnames(data2show))]
data2show <- as.data.frame(data2show)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```


### Metabridge Output

## Lipidomics
### wild type 
#### LFC per class
```{r echo=FALSE}
data2show <- as.data.frame(lipidome$Lipidomics_wt$LFC_Values)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
#### p-Values  per class
```{r echo=FALSE}
data2show <- as.data.frame(lipidome$Lipidomics_wt$stat_res_pVal)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
### knock out
#### LFC per class
```{r echo=FALSE}
data2show <- as.data.frame(lipidome$Lipidomics_ko$LFC_Values)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```
#### p-Values  per class
```{r echo=FALSE}
data2show <- as.data.frame(lipidome$Lipidomics_ko$stat_res_pVal)
DT::datatable(
  data2show,
  extensions = c('Buttons','ColReorder'),
  filter = 'top',
  options = list(
    paging = TRUE,
    searching = TRUE,
    fixedColumns = TRUE,
    colReorder = TRUE,
    autoWidth = TRUE,
    ordering = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  class = "display"
)
```